---
title: "Create Discrete Haz Dataset"
author: "Jesse Lecy"
output:
  html_document:
    theme: readable
    df_print: paged
    highlight: zenburn
    toc: true
    self_contained: false
    number_sections: false
    css: clean.css
---



# LOAD PACKAGES

```{r, warning=FALSE, message=FALSE}

library( foreign )
library( memisc )
library( knitr )
library( dplyr )
library( xtable )
library( stargazer )
library( broom )
library( pander )



```



# BUILD HAZARD DATASET



```{r, warning=FALSE }


dat <- read.dta( "./Data/NCCS-Digitized-Ruledate-1998.dta" )

head( dat ) %>% pander
```


## Summary Stats

```{r}

summary(dat) %>% pander

```



## Original DV

```{r}

table( dat$fisyr, dat$JustNowProfessionalized )

prop.table( table( dat$fisyr, dat$JustNowProfessionalized ), margin=1 )

table( tapply( dat$JustNowProfessionalized, dat$ein, sum, na.rm=T ) )

```



## Create New DV

```{r}


prof <- NULL

fr <- NULL

for( i in unique(dat$ein) )
{
  one.org <- dat[ dat$ein == i , ]
  
  # first.year <- min(one.org$fisyr)
  
  first.rev <- one.org$FS_Totrev_adj[ which.min(one.org$fisyr) ]
  
  fr <- c(fr,first.rev)
  
  if( first.rev > 100000 )
  { 
    spell <- rep(NA, nrow(one.org)) 
    prof <- c( prof, spell )
  }
  
  if(first.rev < 100000 )
  {
    spell <- ifelse( one.org$FS_Totrev_adj < 100000, 0, 1 )
    # drop obs after professionalizes
    num.prof.periods <- cumsum(spell)
    is.prof <- num.prof.periods > 0
    is.prof[ is.prof== F ] <- NA
    post.prof.periods <- duplicated(is.prof, incomparables=NA )
    spell[ post.prof.periods ] <- NA
    
    prof <- c( prof, spell )
  }
  
}



dat <- cbind( prof, dat )

```


```{r}


dd <- dat[ ! is.na(dat$prof ) , ]

dd <- dd[ ! is.na(dd$SurplusRat_ndrop_w892) , ]

# exclude hospital or higher ed

dd <- dd[ ! dd$Subsector2 == "Higher Edu or Hospitals" , ]

nrow( dd )


# First year they apear in the data

table( tapply( dd$fisyr, dd$ein, min ) )

# Length of spells

table( table( dd$ein ))

```



# NEW DV

Create new DV according to the rules:

- Remove the ones that were born big, then dipped, then remained/surged
- If first year of JNP reporting they report less 100k, then change JNP for previous year to zero
- If first year of JNP reporting they report more than 100k, then change JNP for the previous year to 0
- If born over 100k, drop all (even if dip later)
- If currently under 100k, previous year is missing, and year before previous year was also below 100k, then impute the current JNP=0
- If currently over 100k, previous year is missing, and year before previous year was below 100k, then impute the current JNP=1


Here is the sample breakdown:

- 13,440 unique orgs with RULEDATE 1998 in sample
- 5,644 have first-year revenues over $100k
- 7,796 orgs remain in the sample

Length of spells for grassroots orgs:

1 |   2   | 3   | 4 |   5 |   6
==|=======|=====|====|===|=====
1541 | 2404 |  1460 | 1016 |  866 | 509


Which means there are 22,177 rows of data (observation periods). 

There are 14 values in the SurplusRat_ndrop_w892 variable that are missing, so that drops to 22,163.

There are 49 hospitals and universities, accounting for 137 total spells.

After dropping we are down to 22,026.




## Defining Other Study Vars

```{r}


D1 <- ifelse( dat$fisyr == 1998, 1, 0 )
D2 <- ifelse( dat$fisyr == 1999, 1, 0 )
D3 <- ifelse( dat$fisyr == 2000, 1, 0 )
D4 <- ifelse( dat$fisyr == 2001, 1, 0 )
D5 <- ifelse( dat$fisyr == 2002, 1, 0 )
D6 <- ifelse( dat$fisyr == 2003, 1, 0 )


AGE <- dat$age + 1

Age2 <- AGE * AGE

Age3 <- AGE * AGE * AGE

Age4 <- AGE * AGE * AGE * AGE

Age5 <- AGE * AGE * AGE * AGE * AGE



dat <- cbind( dat, D1, D2, D3, D4, D5, D6, AGE, Age2, Age3, Age4, Age5 )

rm( D1, D2, D3, D4, D5, D6, AGE, Age2, Age3, Age4, Age5, prof )

```



## Drop Born Large Orgs

```{r}
# number of nonprofits in sample

length( unique( dat$ein ))

# original number of obs

nrow( dat )


# remove the born large orgs

dat <- dat[ ! is.na(dat$prof) , ]

nrow( dat )

```






## Sanity Check

```{r}

# number of grassroots nonprofits in the sample

length( unique( dat$ein ))

# number that professionalize

sum(dat$prof)

# total proportion that professionalize

sum(dat$prof) / length( unique( dat$ein ))


# check to make sure none professionalize twice

table( tapply( dat$prof, dat$ein, sum ) )


# when do orgs professionalize

table( dat$fisyr, dat$prof )

prop.table( table( dat$fisyr, dat$prof ), margin=1 )

```



## DROP ODD CASES

```{r}


# drop 14 missing Surplus Ratio cases

dat <- dat[ ! is.na(dat$SurplusRat_ndrop_w892) , ]

# exclude hospital or higher ed

dat <- dat[ ! dat$Subsector2 == "Higher Edu or Hospitals" , ]

nrow( dat )


```


## CONVERT EQUITY RATIO TO THOUSANDS

```{r}

# convert EqRat_w to thousands to have meaningful reg coefficients

summary( dat$EqRat_w )

dat$EqRat_w_K <- dat$EqRat_w / 1000


```



# WRITE DATASET

```{r}

write.csv( dat, "./Data/CompleteHazardSpells.csv" )

saveRDS( dat, "./Data/CompleteHazardSpells.rds" ) 

```















